Containers and R: the Rockerverse and beyond

### 2019-10-07 manuscript.Rmd
part about r-db

- Binder
  - [`holepunch`](https://github.com/karthik/holepunch) streamlines making an R research compendium Binder-ready [@karthik]
  - [`repo2docker`](https://repo2docker.readthedocs.io/en/latest/config_files.html) (`install.R`, `DESCRPTION`, `runtime.txt`) based on the Rocker images [@nuest]
- GPU [@noamross, @cboettig]
- Gigantum stack
- in education (ready to use teaching/learning environments)
  - [`r-db`](https://github.com/ColinFay/r-db) [@ColinFay]
- [RCloud](https://github.com/att/rcloud/tree/master/docker) ?

>>>>

- Binder
  - [`holepunch`](https://github.com/karthik/holepunch) streamlines making an R research compendium Binder-ready [@karthik]
  - [`repo2docker`](https://repo2docker.readthedocs.io/en/latest/config_files.html) (`install.R`, `DESCRPTION`, `runtime.txt`) based on the Rocker images [@nuest]
- GPU [@noamross, @cboettig]
- Gigantum stack

R is a fantastic tool when it comes to interfacing with databases: almost every open source and proprietary database system has an R package that allows users to connect and interact with the it 
This flexibility is even broader now that we have tools like `DBI`, that allows to create a common API for interfacing these databases, or like `dbplyr`, which are designed to run `dplyr` code straight against the database. 
But learning and teaching these tools comes with a cost: the cost of deploying or having access to an environment with the softwares and drivers installed. 
For people teaching R, it can become a barrier if they need to install local versions of the drivers, or to connect to remote instances which might or might not be made available by the IT. 
Giving access to a sandbox for the most common database environments is the idea behind [`r-db`](https://github.com/ColinFay/r-db) [@ColinFay], a docker image that contains everything needed to connect, from R, to a database. 
Notably, with `r-db`, the users don't have to install complex drivers or to configure their machine in a specific way. 
On top of that, `r-db` comes with a comprehensive [online guide](http://colinfay.me/r-db/), explaining how to spin a docker instance of a specific database, and how to use `r-db` to connect to it. 
Each package contained inside this image also has a series examples, so that the user can get started with the database right away.

- [RCloud](https://github.com/att/rcloud/tree/master/docker) ?
